
\appendix{Template instructions}


In the HY-CS-main.tex file you will find the following STEPS 0--5. Bellow instructions what each STEP means and how to set up your thesis by following these STEPS.
\vspace{0.5cm}

\textbf{STEP 0 -- Clone the thesis template}

\begin{itemize}
\item One template for all thesis types: \url{https://www.overleaf.com/read/hzgngkgshqwh}
\end{itemize}


{\textbf{STEP 1 -- BSc or MSc thesis?}}
\begin{enumerate}
\item Select whether your are writing BSc (tkt for new, tktl for old) or MSc (csm for new, cs for old, dsm for data science) thesis.
\item Select your language: finnish, english, or swedish.
\item If you are writing MSc select your line / track.
\end{enumerate}


{\textbf{STEP 2 -- Set up your personal information}}

\begin{enumerate}
\item Write the working title of your thesis.
\item Write your name to the author field.
\item Write the names of your supervisors and examiners of the thesis.
\end{enumerate}

{\textbf{STEP 3 -- Write your abstract here}}

\begin{itemize}
\item You can also have the abstract in multiple languages with otherlanguages-environment. Bellow example how to add an english abstract to a thesis written in some other language than english: 

\begin{verbatim}
\begin{otherlanguage}{english} 
\begin{abstract}
Your abstract text goes here. 
\end{abstract} 
\end{otherlanguage}
\end{verbatim}

\end{itemize}

{\textbf{STEP 4 -- Writing your thesis}}

\begin{enumerate}
\item There are some writing instructions in [bsc/msc]\_[finnish/english]\_contents.tex files.
\item You can delete the contents of [bsc/msc]\_[finnish/english]\_contents.tex file and write your thesis inside that file.
\end{enumerate}

{\textbf{STEP 5 -- Set your bibliography style}}

\begin{itemize}
\item The default is Numbering alphabetic order, which should be used in most cases.
\end{itemize}
